%% The following is a directive for TeXShop to indicate the main file
%%!TEX root = diss.tex

\chapter{Acknowledgments}

\bstart{Acknowledgements by chapter}

{\it Chapter~\ref{ch:typology}}: First, I thank my co-author Tamara Munzner, who first conceived this project during her PhD and during early discussions with Fran\c{c}ois Guimbreti\`ere. 
I acknowledge Ron Rensink for the original idea of classifying lookup, browse, locate, and explore according to target identity and location.
I also thank Jessica Dawson, Joel Ferstay, Stephen Ingram, Joanna McGrenere, Miriah Meyer, Michael Sedlmair, and Colin Ware for their feedback on the paper. 
We received financial support for this project from the Natural Sciences and Engineering Research Council of Canada (NSERC). 

{\it Chapter~\ref{ch:drvistasks}}: I thank my co-authors: Michael Sedlmair, Stephen Ingram, and Tamara Munzner; Michael was the first author of the technical report~\cite{Sedlmair2012b} that was the starting point for our 2014 \ac{BELIV} paper~\cite{Brehmer2014b} and this chapter.
I also thank the data analysts who participated in the original interview study for their time and energy: Kerem Altun, Ryan Brinkman, Jennifer B\"uttgen, Anamaria Cri\c{s}an, Klaus Dress, Des Higgins, Carrie Holt, Heidi Lam, Kevin Leyton-Brown, Cindy Marven, Greg Mori, Sareh Nabi-Abdolyousefi, Cydney Nielsen, Ahmed Saad, Jonathan Stray, Sid Thakur, John Westbrook, James Wright, and Hong Yi.
Finally, I thank Steven Bergner, Jessica Dawson, Joel Ferstay, Miriah Meyer, Torsten M\"oller, Tom Torsney-Weir, Melanie Tory, and Hamidreza Younesy for assisting with interviews and/or feedback on paper drafts.
We received financial support for this project from NSERC.

{\it Chapter~\ref{ch:overview}}: I thank my co-authors: Stephen Ingram, Jonathan Stray, and Tamara Munzner. 
I thank Jonas Karlsson and Adam Hooper, who contributed to the development {\it Overview} v3-v4. 
I also thank the case study journalists: Jack Gillum, Ian James, Michael Keller, Adam Playford, Jonathan Stray, Jarrel Wade, and the {\sc dallas} journalist who requested to remain anonymous. 
Finally, I thank Jessica Dawson, Joel Ferstay, Heidi Lam, Joanna McGrenere, Ron Rensink, and Michael Sedlmair for their comments on the project and paper.
We received financial support for this project from the Knight News Challenge and NSERC. 

{\it Chapter~\ref{ch:emu}}: I thank my co-authors: Jocelyn Ng, Kevin Tate, and Tamara Munzner. 
I also thank our collaborators at EnerNOC (formerly Pulse Energy): Bruce Cullen, Ben Gready, David Helliwell, Bruce Herzer, Steve Jones, Jamie King, Sarah Laird, Fritz Lapastora, Ari Lesniak, Jordana Mah, Harish Raisinghani, Maria Serbenescu, Paul Teehan, and especially James Christopherson.
I also especially thank Cailie Crane, Reetu Mutti, and the Energy Manager development team. 
I also thank the energy analysts that we interviewed: Marc Etienne Brunet, Andy Constant, Bill Edbrooke, Chris Goodchild, Marc Tabet, Sean Terry, Natalie Vadeboncoeur, Lillian Zaremba, and especially Jerome Conraud and Kevin Ng. 
Finally, I thank Michelle Borkin, Anamaria Cri\c{s}an, Jessica Dawson, Johanna Fulda, Enamul Hoque, Sung-Hee Kim, Narges Mahyar, and Joanna McGrenere for their feedback on the paper.
We received financial support for this project from NSERC and Mitacs. 

For each of the four research chapters, I thank the anonymous reviewers who reviewed the associated research paper, and in particular I thank the reviewer of our typology paper~\cite{Brehmer2013} who introduced me to {\it Cognitive Work Analysis} by \citet{Vicente1999}, which proved to be an excellent resource.

\bstart{Personal acknowledgements}

First and foremost, I thank Tamara Munzner, my primary thesis advisor, who first reached out to me during the 2009 graduate recruitment season, taught me the principles of visualization analysis and design in her graduate course later that year, and took me on as a PhD student in 2011. 
I thank her for all of our discussions, her attention to detail, and the career mentoring that she has provided over the last several years.

I thank Joanna McGrenere, my co-advisor. 
Joanna encouraged me to pursue a PhD, and has since provided thoughtful mentoring and perspectives on HCI research.

I thank Ron Rensink, the third member of my supervisory committee. I am particularly thankful for Ron's graduate seminar in visual display design, which provided dual perspectives from perceptual psychology and design, as well as opportunities to practice succinct writing and peer review.

I thank my external examiner Jason Dykes for his very thorough report and the thought-provoking questions that he raised.

I thank my university examiners Giuseppe Carenini and Alfred Hermida, as well as my thesis defense chair Luanne Freund.

I thank Giuseppe Carenini, chair of my thesis proposal defense meeting in 2014, and Ron Garcia, chair of my research proficiency evaluation meeting in 2012.

I thank the members of the Tamara Munzner's InfoVis group between 2011 and 2016: Michelle Borkin, Anamaria Cri\c{s}an, Jessica Dawson, Kimberly Dextras-Romagnino, Wenqiang (Dylan) Dong, Joel Ferstay, Johanna Fulda, Stephen Ingram, Zipeng Liu, and Michael Sedlmair. 
I also thank regular group meeting attendees Giuseppe Carenini, Enamul Hoque, Sung-Hee Kim, and Narges Mahyar, as well as group alumni Heidi Lam, Miriah Meyer, and Melanie Tory who joined in person or remotely for occasional meetings.

I thank the members of Joanna McGrenere's LUNCH (Lab for Universal usability, persoNalization, {\sc Cscw}, and {\sc Hci}) research group between 2011 and 2016: Kamyar Ardekany, Jessica Dawson, Shathel Haddad, Mona Haraty, Sung-Hee Kim, Juliette Link, Matei Negulescu, Antoine Ponsard, Diane Tam, Charlotte Tang, and Kailun Zhang.

I thank the members of the UBC MUX (Multimodal User eXperience) lab between 2011 and 2016 for the feedback and support they provided during research update presentations and practice talks. 
In addition to all of those already mentioned above from the InfoVis and LUNCH groups, I thank faculty members Kellogg Booth and Karon MacLean, as well as all the post-docs, visiting researchers, and students who have contributed to the culture of the MUX lab.

I thank the InfoVis subcommittee of the 2014 IEEE Doctoral Colloquium for their feedback on my thesis research program: Christopher Collins, Petra Isenberg, and Chris Weaver. 
I also thank my fellow Doctoral Colloquium participants: Sriram Karthik Badam, Richard Brath, Samuel Gratzl, Julia J\"urgens, and Jorge Poco.

I also thank those that I collaborated and co-authored with on other projects between 2011 and 2016: Benjamin Bach, Johanna Fulda, Nathalie Henry Riche, Claudia Jacova, Joanna McGrenere, Charlotte Tang, Melanie Tory, Sheelagh Carpendale, Donghao Ren, and especially Bongshin Lee.

I thank Eamonn Maguire for the excellent illustrations that he created for Tamara's book~\cite{Munzner2014} and for making it possible for me to use them in this dissertation.

I thank Sandra Mathison, instructor of EPSE 595 (a qualitative research methods course offered in Winter 2012), who introduced me to a number of epistemological and theoretical perspectives, methodologies, and methods.

I thank Laura Selander, group assistant for the UBC Imager lab, and Joyce Poon, UBC Department of Computer Science graduate program assistant, for their logistics support.

I thank Joanna McGrenere and Claudia Jacova, my M.Sc advisors, as well as T. C. Nicholas Graham, my undergraduate honours thesis advisor; my decision to pursue a PhD was in part motivated by my early research experiences with them and by their encouragement. 

I thank my family for all of their love and support over the years: my parents Leslie and Michael Brehmer, my brother Nicholas Brehmer, my grandparents, and my uncle Thomas Brehmer, who introduced me to the work of Edward Tufte at an impressionable age.

Lastly, I thank my partner, Anamaria Cri\c{s}an: for enduring, for understanding, and for joining me on this path.
